A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Final changes

Let $O$ be the origin of the camera in the scene. For each pixel $P$ of the final image, let $x$ be the nearest intersection point of the ray $(O, \overrightarrow{OP} = -\Theta)$ with an element of the scene. To obtain the luminosity, we must solve the rendering equation \cite{Ka86} which is a recursive integral equation. The integrand of the equation contains the radiance function that we must compute:

@@

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$. $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at point $x$.

This integrand expresses an intuitive idea: the reflected radiance from $x$ towards the camera is the result of computing all incoming luminosity on $x$ scaled by a factor which depends on the material on $x$ and the angle of the ray going from the camera to $x$. The most common method used to estimate the integral, denoted by $L_r(x \rightarrow \Theta)$, is the Monte-Carlo integration which provides the following:

@@

where $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the choosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. give high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling} and is used in global illumination to improve the convergence speed of the algorithms.

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reached.

This computation is done multiple times for each pixel (at different positions over the pixel). We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
A bad pdf would lead in picking directions that don't reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because it is an input of the algorithm.
The term $L$, which represents the distribution of light in the scene, is unknown. Our method gives a way to sample according to $L$.

@@

%La, pas clair !!!
Let $L$ be a light source of the scene and $n_L$ the nearest node of the skeleton that is visible by $L$. For each node, we compute the shortest path to $n_L$ along the skeleton. To do so, we use the Dijkstra algorithm and weight the edges of the skeleton depending on a visibility criteria: the weight of an edge $e$ is $1$ if $e$ is visible from $n_L$ and $10$ else. It results that the paths that are illuminated by a light will be shorter than paths located in dark areas.

@@

\subsection{Results and discussion}

Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produce less noisy images compared to the regular path tracing. We present, in table~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes.

@@

\begin{figure}[tb]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & Corridor & Sponza 1 & Sponza 2 (Fig. \ref{fig:results}) \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Time to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right is for our method}
\label{tab:timing}
\end{figure}

>>>>

Let $O$ be the origin of the camera in the scene. For each pixel $P$ of the final image, let $x$ be the nearest intersection point of the ray $(O, \overrightarrow{OP} = -\Theta)$ with an element of the scene. To obtain the luminosity, we must solve the rendering equation \cite{Ka86} which is a recursive integral equation, the integrand containing the radiance function that we must compute:

@@

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$ and $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at point $x$.

The previous equation expresses an intuitive idea: the reflected radiance from $x$ towards the camera is the result of computing all incoming luminosity on $x$ scaled by a factor which depends on the material on $x$ and the angle of the ray going from the camera to $x$. The most common method used to estimate the integral, denoted by $L_r(x \rightarrow \Theta)$, is the Monte-Carlo integration which provides the following:

@@

The function $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the choosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. give high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling}~\cite{Ka86} and is used in global illumination to improve the convergence speed of the algorithms.

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when either a maximal number of bounces or a directly illuminated area have been reached.

This computation is done multiple times for each pixel. We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
A bad pdf would lead in picking directions that don't reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because it is an input of the algorithm.
The term $L$, which represents the distribution of light in the scene, is unknown. Our method gives a way to sample $L$.

@@

%La, pas clair !!!
Let $L$ be a light source of the scene and $n_L$ the nearest node of the skeleton that is visible by $L$. For each node, we compute the shortest path to $n_L$ along the skeleton. To do so, we use the Dijkstra algorithm and weight the edges of the skeleton depending on a visibility criteria: the weight of an edge $e$ is $1$ if $e$ is visible from $n_L$ and $10$ else. It results that illuminated paths will be shorter than paths located in dark areas.

@@

\subsection{Results and discussion}
Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produces less noisy images compared to the regular path tracing. We present, in Fig~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes: our method is the fastest.

@@

\begin{figure}[tb]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & Corridor & Sponza 1 & Sponza 2 (Fig. \ref{fig:results}) \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Time (s) to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right is for our method}
\label{tab:timing}
\end{figure}

### 2012-09-14 skeleton_and_pathtracing.tex
Change a image
Final changes

A path tracing algorithm sends rays from the camera, and let them bounce around the scene until they encounter a directly illuminated zone. When a ray hits a point of any surface, it is reemitted in a random direction. Once a ray reaches a directly illuminated area, all luminance gathered through its journey in the scene is averaged in order to set the color one of the pixels of the image, and the process is repeated for each pixel of the output image. To avoid the noise resulting from this stochastic process, the algorithm actually sends, for each pixel of the image, many rays: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

In order to avoid infinite bouncing of rays in the scene, a limit is set for the number of bounces a ray can do. If a ray does not reach any directly illuminated area after a given number of bounces, its contribution is null. Such lost ray is as a waste of computation time, and minimizing this loss would speed up the algorithm.

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources, thus reducing the number of rays \quotes{lost} during the computation. To do this, we perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on towards which direction a ray should bounce in order to meet a light source. Unfortunately, such precomputation may take time and become more expensive than the original algorithm.

To keep the precomputation fast, we perform it only on a subset of points of the voids of the scene. The precomputation we want to perform relies on paths and visibility tests, therefore want this set of points to be representative of both the topology and the geometry of the original scene. For example, it should possess branches propagating in the elongated parts of the scene. A filtered curvilinear skeleton of (the voids of) the scene meets all the required properties for our subset of points: it is a thin subset of points of the scene, with the same topology and retaining the main geometrical information of the scene. Note that in this application, the filtering of the skeleton (elimination of spurious branches) need to be both efficient and completely automatic, for one cannot ask a user to set parameters for each scene.

@@

\caption{\label{fig::intro_image} Images $a$ and $b$ shows some rays of the path tracing guided by the material of the objects (image $a$) or our skeleton based method (image $b$). Images $c$ and $d$ point out the noise reduction between the classic path tracing (image $c$) and our method (image $d$).}
\end{center}
\end{figure}

The purpose of this paper is twofold: we first introduce a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). 
Then, we expose a new method, based on such skeletons, to enhance the results and the performance of the path tracing algorithm (see Sec.~\ref{sec::appli_pathtrace}).

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{ccccc}
	\myincludegraphics{0.19\textwidth}{invader.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step1_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step2_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step3.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step4.pdf} \\
\end{tabular}
\caption[Four first iterations of Alg.~\ref{algo::pardircollapse_v0}]{\label{fig::example_algo} \textbf{Four first iterations of Alg.~\ref{algo::pardircollapse_v0}} running on the left-most shape.}
\end{center}
\end{figure}

@@

Generally, two strategies are possible to achieve this goal: find, during the skeletonization process, points whose neighbourhood configuration seems interesting and keep them in the result \cite{CouCoeurZrour07} \cite{HR08} \cite{CCT09ext}), or choose, before skeletonization, interesting points of the object which should remain untouched, based on a function on these points and a filtering parameter \cite{BertrandCouprie06} \cite{Pal07}.

Algorithm ~\ref{algo::pardircollapse_v0} does not necessarily preserve geometrical features of the input object in the resulting skeleton, which end up being a single vertex.

In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: its finds, during thinning, elements whose neighbourhood configuration is interesting, and uses a function on these elements to decide to preserve them in the result.

>>>>

A path tracing algorithm sends rays from the camera, and let them bounce around the scene until they encounter a directly illuminated zone. When a ray hits a point of any surface, it is reemitted in a random direction. Once it reaches a directly illuminated area, all luminance gathered through its journey in the scene is averaged in order to set one of the image pixels, a process repeated for each pixel of the output image. To avoid the noise resulting from this stochastic process, the algorithm actually sends many rays for each pixel of the image: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

In order to avoid infinite bouncing of rays in the scene, a limit is set for the number of bounces a ray can do. If a ray does not reach any directly illuminated area after a given number of bounces, its contribution is null. Such lost ray is a waste of computation time, and minimizing this loss would speed up the algorithm (see Fig~\ref{fig::intro_image}.a).

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources (see Fig~\ref{fig::intro_image}.b), thus reducing the number of rays \quotes{lost} during the computation. To do this, we perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on the direction a ray should bounce in order to meet an illuminated area. Unfortunately, such precomputation may take time and become more expensive than the original algorithm.

To keep the precomputation fast, we perform it only on a subset of points of the voids of the scene. Since this precomputation relies on paths and visibility tests, we want this set of points to be representative of both the topology and the geometry of the original scene. For example, it should possess branches propagating in the elongated parts of the scene. A filtered curvilinear skeleton of the scene's void meets all the required properties for our subset of points: it is a thin subset of points, with the same topology and retaining the main geometrical information of the scene. Note that in this application, the filtering of the skeleton (elimination of spurious branches) need to be both efficient and completely automatic, for one cannot ask a user to set parameters for each scene.

@@

\caption{\label{fig::intro_image} Note how rays are guided toward the illuminated area thanks to our skeleton based algorithm (image $b$), compared to classical path tracing (image $a$). Images $c$ and $d$ point out the noise reduction between the classic path tracing ($c$) and our method ($d$).}
\end{center}
\end{figure}

The purpose of this paper is twofold: we first introduce a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). 
Then, we expose a new method, based on such skeletons, to enhance the results (see Fig~\ref{fig::intro_image}.c and d) and the performance of the path tracing algorithm (Sec.~\ref{sec::appli_pathtrace}).

@@

\begin{figure}[bth]
\begin{center}
\begin{tabular}{ccccc}
	\myincludegraphics{0.19\textwidth}{invader.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step1_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step2_2.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step3.pdf} &
	\myincludegraphics{0.19\textwidth}{invader_step4.pdf} \\
\end{tabular}
\caption[Four first iterations of Alg.~\ref{algo::pardircollapse_v0}]{\label{fig::example_algo} \textbf{Four first iterations of Alg.~\ref{algo::pardircollapse_v0}} running on the left-most shape.}
\end{center}
\end{figure}

@@

Generally, two strategies are possible to achieve this goal: find, during the skeletonization process, points whose neighbourhood configuration seems interesting and keep them in the result \cite{CouCoeurZrour07} \cite{HR08} \cite{CCT09ext}, or choose, before skeletonization, interesting points of the object which should remain untouched, based on a function on these points and a filtering parameter \cite{BertrandCouprie06} \cite{Pal07}.

Algorithm~\ref{algo::pardircollapse_v0} does not necessarily preserve geometrical features of the input object in the resulting skeleton, which end up being a single vertex.

In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: its finds, during thinning, elements whose neighbourhood configuration is interesting, and uses a function on these elements to decide to preserve them, or not, in the result.
